Enhancing Student Engagement via Reduction of Frustration with Programming Assignments using Machine Learning

### 2017-02-14 paper.tex
De-anonymizing

\section{Experiment}
\label{sec:exp}
The aim of this research is to evaluate the use of keyboard
and mouse dynamics as an appropriate sensory input for an affective recognition
system. The context of use is a learning environment for programmers. In
particular for learning activities consisting in writing short programs
interactively. An experimental approach was adopted with this aim: Sensory and
quantitative data was collected from learners as they were enrolled in a basic
course of Python programming. This data was then pre-processed using the method
described earlier in Section \ref{sec:method}, and together with the quantitative data obtained from users,
classifiers were trained and validated. The results were then compared
and we arrived to some conclusions regarding the effectiveness of the method. The goal given to
subjects was to solve as many exercises as they could in a period of two weeks.
There was neither time limit nor a minimum amount of time required for a
participant while trying to solve the exercises or complete the tutorial. The
participants were able to stop and resume their interaction with the system at
any time.

\begin{figure}[!t] 
\centering 
\includegraphics[width=2.5in]{Completed.png} 
\caption{Completed activities and exercises and by learner in ascending order.}
\label{fig_completed} 
\end{figure}

\begin{figure}[!t] 
\centering 
\includegraphics[width=2.5in]{classDist.png} 
\caption{Class distribution of emotions as reported by learners.}
\label{fig_class} 
\end{figure}

@@

% use section* for acknowledgment 
\section*{Acknowledgment} This work received funding from some places, but this is 
only to keep the needed space this is only to keep the space.

% trigger a \newpage just before the given reference 
% number - used to balance the columns on the last page 
% adjust value as needed - may need to be readjusted if 
% the document is modified later %\IEEEtriggeratref{8} 
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

>>>>

\section{Experiment}
\label{sec:exp}
The aim of this research is to evaluate the use of keyboard
and mouse dynamics as an appropriate sensory input for an affective recognition
system. The context of use is a learning environment for programmers. In
particular for learning activities consisting in writing short programs
interactively. An experimental approach was adopted with this aim: Sensory and
quantitative data was collected from learners as they were enrolled in a basic
course of Python programming. This data was then pre-processed using the method
described earlier in Section \ref{sec:method}, and together with the quantitative data obtained from users,
classifiers were trained and validated. The results were then compared
and we arrived to some conclusions regarding the effectiveness of the method. The goal given to
subjects was to solve as many exercises as they could in a period of two weeks.
There was neither time limit nor a minimum amount of time required for a
participant while trying to solve the exercises or complete the tutorial. The
participants were able to stop and resume their interaction with the system at
any time.
%
\begin{figure}[!t] 
\centering 
\includegraphics[width=2in]{Completed.png} 
\includegraphics[width=2in]{classDist.png} 
\caption{Completed activities and exercises and by learner in ascending order (left) and lass distribution of emotions as reported by learners (right).}
\label{fig_completed} 
\end{figure}

@@

% use section* for acknowledgment 
\section*{Acknowledgment} 
This work has been supported in part by: de Ministerio espa\~{n}ol de Econom\'{\i}a y Competitividad under project TIN2014-56494-C4-3-P (UGR-EPHEMECH).
